An Improved Method for Coupling Hydrodynamics with Astrophysical Reaction Networks

### 2021-12-29 simplified_sdc_intro/paper.tex
finish first cut at the sub ch

To quantify this effect, we next looks at the total mass of some key species.
This is often a desired diagnostic for supernova calculations, since 
\isot{Ni}{56} powers the lightcurve.  Table \ref{table:masses} shows the total
mass of \isot{He}{4}, \isot{Si}{28}, and \isot{Ni}{56} for each of the
simulations.

>>>>

To quantify this effect, we next looks at the total mass of some key
species.  This is often a desired diagnostic for supernova
calculations, since \isot{Ni}{56} powers the lightcurve.  Table
\ref{table:masses} shows the total mass of \isot{He}{4},
\isot{Si}{28}, and \isot{Ni}{56} for each of the simulations.  For the
Strang runs, there are large variations between the different
simulations while the SDC simulations all agree to within a few
percent.  Further, the Strang run with the tighter tolerances is in
good agreement with the masses found by the SDC runs.  This supports
the ideas described above that all of the SDC runs agree while only
the Strang run with the tighter tolerances is reliable.

\begin{deluxetable}{llll}
\tablecaption{\label{table:masses} Species masses.}
\tablehead{\colhead{simulation} & \colhead{$M_{\isotm{He}{4}}$} & \colhead{$M_{\isotm{Si}{28}}$} & \colhead{$M_{\isotm{Ni}{56}}$}}
\startdata
\multicolumn{4}{c}{Strang runs} \\
\hline
{\tt strang\_subch2\_cfl0.2}           & $6.10\times 10^{31}$ & $6.72\times 10^{31}$ & $5.29\times 10^{31}$ \\
{\tt strang\_subch2\_cfl0.4}           & $5.20\times 10^{31}$ & $6.70\times 10^{31}$ & $6.02\times 10^{31}$ \\
{\tt strang\_subch2\_cfl0.4\_mixedtol} & $3.05\times 10^{31}$ & $7.29\times 10^{31}$ & $7.80\times 10^{31}$ \\
{\tt strang\_subch2\_cfl0.8}           & $4.59\times 10^{31}$ & $6.88\times 10^{31}$ & $6.27\times 10^{31}$ \\
\hline
\multicolumn{4}{c}{SDC runs} \\
\hline
{\tt sdc\_subch2\_cfl0.2}           & $3.35\times 10^{31}$  & $7.26\times 10^{31}$  & $8.27\times 10^{31}$ \\
{\tt sdc\_subch2\_cfl0.4}           & $3.30\times 10^{31}$  & $7.27\times 10^{31}$  & $8.13\times 10^{31}$ \\
{\tt sdc\_subch2\_cfl0.4\_mixedtol} & $3.09\times 10^{31}$  & $7.36\times 10^{31}$  & $8.08\times 10^{31}$ \\
{\tt sdc\_subch2\_cfl0.4\_tol1.e-6} & $3.25\times 10^{31}$  & $7.27\times 10^{31}$  & $8.25\times 10^{31}$ \\
{\tt sdc\_subch2\_cfl0.8}           & $3.18\times 10^{31}$  & $7.34\times 10^{31}$  & $7.83\times 10^{31}$ \\
\enddata
\end{deluxetable}
